Draft Report Modelleren-B

### 2021-06-17 Reports/draft_report.tex
Added text

\newpage
\section*{Summary}
\addcontentsline{toc}{section}{Summary}
In this project we explored the world of parcel delivery. Based on a dataset provided we explored various option to optimize the cost of delivering a parcel, this cost optimization was done by building or not building hubs near certain cities. The first algorithm applied was an intuitive algorithm it does not guarantee the optimal solution, but it does give a reasonable solution. The other algorithm applied was an ILP which is takes a lot longer to run but does give the best possible solution.

@@

    After obtaining a function which calculates the cost of assigning hubs to cities, an intuitive algorithm can be made which tries to give an approximation of the combination of hubs that will result in the lowest possible amount of money that the company will have to spend when moving packages. 
    Since the intuitive algorithms are inherently less accurate than a standardized solver, the different aspects of moving packages are split up and solved using different types of algorithms. Hereby, the goal is to minimize the error that the functions have by eventually combining multiple intuitive algorithms such that a minimum cost can be achieved. The total process is divided into the collection from the cities to the hubs, followed by the transfer between hubs themselves, and as last the distribution of packages from the hubs to the desired cities. 
    % we moeten misschien nog even de namen van 2.3 2.5 enzo aanpassen aangezien het originele idee van het opsplitsen van collection, transer en distribution  niet meer van toepassing is
    \subsection{Collection of packages}  
    \label{Collection of packages}
    In this process the cost function will only give an output of the cost that is formed by combining the cost for collecting packages. To optimize the costs a python script is made such that, when a city is given to be a hub, the code calculates the cost for this specific hub and the cost if the city next in line would be a hub as well. If the total cost drops by adding city as a hub, this city will be added to list of cities that are hubs. If the cost rises, the city will be discarded from the process. If this process is repeated with each time a different starting node, a list will appear of possible combination of hubs and their costs. To illustrate this process the outputs will be stated below if it were to start with city number 3 as a hub.

    \begin{table}[h!]
        \begin{center}
            \begin{tabular}{||c |c||} 
                \hline
                Cost of the combination(€ x 10^3) & combination on cities as hubs \\ [0.5ex] 
                \hline\hline
                169.3 & [3,1]  \\ 
                \hline
                169.8 & [3,2]  \\
                \hline
                169.8 & [3,4]  \\
                \hline
                127.2 & [3,5]  \\ 
                \hline
                132.0 & [3,5,6]  \\
                \hline
                127.4 & [3,5,7]  \\
                \hline
                128.5 & [3,5,8]  \\
                \hline
                124.8 & [3,5,9]  \\
                \hline
                118.7 & [3,5,9,10]  \\
                [1ex] 
                \hline
              \end{tabular}
          \end{center}
        \caption{Exampled of the algorithm which adds cities one by one as hubs based on the cost}
        \label{Collection Algorithm}
    \end{table}

@@

            \begin{table}[h!]
                \begin{center}
                \begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|}
                    \hline
                    \multicolumn{3}{|c|}{Amount of times cities are used as hubs} \\
                    \hline
                    City used as hub & Using only collection cost & Using total cost\\
                    \hline
                    1 &  8 & 5 \\
                    \hline
                    2 & 4   & 11 \\
                    \hline
                    3& 7 & 9\\
                    \hline
                    4  & 1 & 1 \\
                    \hline
                    5 & 8 & 9\\
                    \hline
                    6 & 1 & 8   \\
                    \hline
                    7 & 2& 3 \\
                    \hline
                    8 & 2 & 2 \\
                    \hline
                    9 &  7& 10 \\
                    \hline
                    10 & 11 & 11 \\
                    \hline
                    11 & 1& 2 \\
                    \hline
                    12 & 1 & 1 \\
                    \hline
                    13 & 2& 2 \\
                    \hline
                    14 & 14& 14 \\
                    \hline
                \end{tabular}
                \end{center}
                \caption{Table of the amount of times each city is used as a hub in every combination using the large data set}
                \label{amount of times hubs are used in collection} 
            \end{table}

@@

            When the algorithm is used for different input combinations based on ~\ref{amount of times hubs are used in collection} the outputs and results show different possible answers with supposedly relative low cost. Hereby the algorithm will add a city as hub if this results in a lower cost by the principle given in the beginning of the section.

            \begin{table}[h!]
                \begin{center}
                    \begin{tabular}{ |p{3cm}|p{3cm}|p{4cm}|}
                        \hline
                        \multicolumn{3}{|c|}{Cost and combination of hubs with certain input} \\
                        \hline
                        Input into the algorithm & Output -  collection Cost (€ x 10^3) & Output - total Cost (€ x 10^3)\\
                        \hline
                        [14] &  92.6 | [14, 1, 3] & 166.4 | [14, 1, 2, 3, 5, 7]  \\
                        \hline
                        [10] & 90.0 | [10, 2, 14]   & 153.0 | [10, 2, 14, 8] \\
                        \hline
                        [6, 10]& 93.9 | [6, 10, 14] & 150.4 |  [6, 10, 14]\\
                        \hline
                        [6, 14] &  82.9 | [6, 14]  &  144.5 | [6, 14, 8] \\
                        \hline
                        [9, 14] &  100.7| [9, 14, 1, 3] & 160.4 |  [9, 14, 2, 3, 7] \\
                        \hline
                        [2, 14] & 87.6 | [2, 14, 6] & 156.9 |  [2, 14, 3, 6]\\
                        \hline
                        [2, 10, 14] & 90.0 | [2, 10, 14] & 153.0 | [2, 10, 14, 8]  \\
                        \hline
                    \end{tabular}
                \end{center}
            \caption{Table of the amount of times each city is used as a hub in every combination}
            \label{amount of times hubs are used in collection} 
            \end{table}

@@

             \begin{table}[h!]
                \begin{center}
                \begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|}
                    \hline
                    \multicolumn{3}{|c|}{Amount of times cities are used as hubs} \\
                    \hline
                    City used as hub & Using only collection cost & Using total cost\\
                    \hline
                    1 &  8 & 5 \\
                    \hline
                    2 & 4   & 11 \\
                    \hline
                    3& 7 & 9\\
                    \hline
                    4  & 1 & 1 \\
                    \hline
                    5 & 8 & 9\\
                    \hline
                    6 & 1 & 8   \\
                    \hline
                    7 & 2& 3 \\
                    \hline
                    8 & 2 & 2 \\
                    \hline
                    9 &  7& 10 \\
                    \hline
                    10 & 11 & 11 \\
                    \hline
                \end{tabular}
                \end{center}
                \caption{Table of the amount of times each city is used as a hub in every combination with the small data set}
                \label{amount of times hubs are used in collection} 
            \end{table}

    \subsection{Transfer between hubs} \label{sssec:num1}
        Transport to the same node is free if the node is a hub. To optimize the total cost an algorithm is made that will look at the node with the most flow of parcels to itself and makes a hub of this node. After calculating the cost, the next hub with the most flow of parcels to itself will be become a hub. If the solution becomes cheaper by adding a hub, the node is added to a list of hubs. If the total cost increases, nothing happens and the next node (most parcels to itself) becomes a hub. If there are two nodes with the same amount of parcels to itself the algorithm will choose the node with the most incoming parcels. Each node will be connected to the hub with the least cost to transport it there, for example if it cost 11 dollars to transport from node 11 to hub 14 and 27 dollars to transport it to hub 2, node 11 will be connected with hub 14. This process is repeated until the algorithm goes through all nodes. To illustrate we will use the Large and small data assignment.
\subsubsection{Result of the large data set}
        \begin{table}[h!]
            \begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|}
                \hline
                nodes that are hubs & flow of parcels to itself (last node) & Total cost (€ x 10^3)\\
                \hline
                [14] &  181 & 182.7 \\
                \hline
                [14,2]   & 39 & 163.5 \\
                \hline
                [14,2,15] & 26 & 169.3 \\
                \hline
                [14,2,15,6]  & 18 & 156.5 \\
                \hline
                [14,2,15,6,13] & 18 & 161.5\\
                \hline
                [14,2,15,6,13,4] & 11 & 167.0   \\
                \hline
                [14,2,15,6,13,4,3] & 9 & 177.1   \\
                \hline
                [14,2,15,6,13,4,3,9] & 9 & 187.7    \\
                \hline
            \end{tabular}
        \caption{Table of nodes that were used as hubs and the associated costs}
        \end{table}

The cheapest situation here is where there are 4 hubs in nodes 2,6,14 and 15. We connect each node with the hub where the cost to transport a parcel is the lowest, the total cost in this situation would be €156.5 thousand. One can easily see that it is very profitable to make a hub out of node 14, as it is the node with the most incoming parcels (610). In the following subsections we will be looking at the results of the other algorithms and combine those to see if there are similarities.
\subsubsection{Result of the small data set}
(The results of the small data set are still being worked on, though this will be done identically to the large data set.)

@@

As can be seen, the distribution costs decrease with each added hub until they reach 0. This is a result of distribution costs from hubs to themselves costs 0. So more of the actual costs are made up of transfer costs as more hubs get added. However, the total costs, displayed in the last column, have quite different results. At first, the costs decrease. But, after adding hub 9 the total costs increase from there onward. So, based on these results, a solution would be to pick hubs 2, 8, 10 and 14 with a total cost of 152974.

@@

\caption{\centering Order in which the cities got added as hubs by the algorithm based on total costs}
\label{DistAlg2}
\end{table}
\subsubsection{Result of the small data set}
(The results of the small data set are still being worked on, though this will be done identically to the large data set.)

@@

    \subsection{Result of the combined algorithms}
    \subsubsection{Result of the large data set}
By combining and analysing the results of the different algorithms, a hub will be opened at nodes 14 and 6 as these nodes were also hubs in the cheapest situation of all different algorithms that were used. By opening a hub at node 14 the cost for collecting , transferring and distributing can be reduced, as it is the node with the most amount of incoming parcels. The total cost in this situation where we only have two hubs is €144.870. The intuitive algorithm will then go through the nodes one by one and check which combination (with node 14 and 6) is the cheapest, this node will then be added to the list of hubs. This process is repeated until the algorithm goes through all nodes.

\begin{table}[h]
\begin{tabular}{||c |c||}
\hline
Nodes that are hubs & Total cost (€ x 10^3)\\
\hline
[6,14] &  144.8 \\
\hline
[6,8,14]   & 144.5\\
\hline
[2,6,8,14] & 148.1 \\
\hline
[2,5,6,8,14]  & 152.5  \\
\hline
[2,5,6,8,12,14] & 160.3 \\
\hline
\end{tabular}
\caption{Table of nodes that were used as hubs in the initiative algorithm}
\end{table}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[main/.style = {draw, circle,minimum size=0.8cm}]
\node[main] (6) {6};
\node[main] (8) [below right=1.5cm of 6] {8};
\node[main] (14) [below left=1.5cm of 6] {14};

@@

\subsubsection{Result of the small data set}
(The results of the small data set are still being worked on, though this will be done identically to the large data set.)

@@

\subsection{ILP implementation}
For the implementation of the ILP the actual values of the inputs will not be used, rather variables to represent any valid input for the ILP. The actual values can be found in <add ref>. A network of n nodes given by the set N represent the city. A city i $\in$ N can be transformed into a hub with cost $f_i$. The amount of packages sent, or flow, from a city i $\in$ N and a city j $\in$ N is given by $w_{ij}$. The cost to send one unit of flow from a city i $\in$ N to a city j $\in$ N is given by $c_{ij}$. It is important to note that the costs are symmetric. That is, $c_{ij} = c_{ji}$ for all i,j $\in$ N. But the flow is not necessarily symmetric. Lastly, there are multipliers for collecting (from city to hub), transfer (from hub to hub) and distribution (from hub to city). These are given the names $\chi$, $\alpha$, $\delta$ respectively.

@@

Next, a means is required that indicates which path is valid for a package to take from a city i to j. A way to do this is by requiring that, for some i,j,k,l \in N, both $e_{ik} = 1$ and $e_{lj} = 1$. However, this would not be linear. Instead we introduce a helper variable $y_{ijkl}$ to mean the same as that:

@@

To make this variable mean the same as what is desired, the following three constraints are introduced:

\begin{align*}
    y_{ijkl} &\leq e_{ik} \\
    y_{ijkl} &\leq e_{jl} \\
    y_{ijkl} &\geq e_{ik} + e_{jl} - 1
\end{align*}

The validity of these constraints is shown in table \ref{tab:Helper}.

@@

With this helper variable defined it is now possible to construct the objective function. First of all, the cost for a unit of flow sent along a certain path is needed. Given a path from $i \rightarrow k \rightarrow l \rightarrow j$ with i,j,k,l $\in$ N and the relevant multipliers we get that sending one unit of flow over this path is $\chi c_{ik} + \alpha c_{kl} + \delta c_{lj}$. However, we want to send more than just one package. So, it is multiplied by the total flow between the sending city i and receiving city j, namely $w_{ij}$. To make sure that the chosen path is valid, that is city i is assigned to hub k and city j is assigned to hub l, it is also multiplied by $y_{ijkl}$. Summing over i,j,k,l $\in$ N, the total costs for sending packages over the chosen hubs and connections is: 
$$\sum^N_{i=1}\sum^N_{j=1}\sum^N_{k=1}\sum^N_{l=1} w_{ij}(\chi c_{ik} + \alpha c_{kl} + \delta c_{lj})y_{ijkl}$$

On top of that, there is also the costs of establishing hubs at certain cities. We multiply this cost for a certain city k $\in$ N by $e_{kk}$, since only hubs are connected to themselves. Summing over k, this gives the total cost of establishing the hubs as:
$$\sum^N_{k=1} f_k e_{kk}$$

>>>>

\newpage
\section*{Summary}
\addcontentsline{toc}{section}{Summary}
In this project we explored the world of parcel delivery. Based on a dataset provided we explored various option to optimize the cost of delivering a parcel, this cost optimization was done by building or not building hubs near certain cities. The first algorithm applied was an intuitive algorithm it does not guarantee the optimal solution, but it does give a reasonable solution. The intuitive algorithm worked by iteratively finding the hub that would give the lowest cost and adding that to the list of hubs. So the program would find the hub that would minimize cost and add it to the list, for example 14 then it would go through all hubs again and find for example that 8 would minimize cost. This would repeat till adding an extra hub would not lower cost any more. The other algorithm applied was an ILP which is takes a lot longer to run but does give the best possible solution.

Interestingly, the results of the ILP solver came very close to the results of the intuitive algorithm. Both the ILP and the intuitive algorithm gave as the optimal solution that cities 14,8,6 should be hubs for a total cost of 144.522 euros. The only difference between the result of the ILP and the Intuitive algorithm is that ILP connected city 10 with hub 6 whilst the intuitive algorithm connected that city with hub 14. This difference was only 163 euros.

To extend the problem, we wanted to make the model more realistic. We looked at what if the amount of packages would be limited by the capacity of a transport bus. So instead of using multipliers which we used in the original problem we capped the maximum amount a bus could carry and determined the cost by the amount of transport busses necessary.

@@

    After obtaining a function which calculates the cost of assigning hubs to cities, an intuitive algorithm can be made which tries to give an approximation of the combination of hubs that will result in the lowest possible amount of money that the company will have to spend when moving packages. 
    Since the intuitive algorithms are inherently less accurate than a standardized solver, the different aspects of moving packages are split up and solved using different types of algorithms. Hereby, the goal is to minimize the error that the functions have by eventually combining multiple intuitive algorithms such that a minimum cost can be achieved. The total process is divided into the collection from the cities to the hubs, followed by the transfer between hubs themselves, and as last the distribution of packages from the hubs to the desired cities. 
    % we moeten misschien nog even de namen van 2.3 2.5 enzo aanpassen aangezien het originele idee van het opsplitsen van collection, transer en distribution  niet meer van toepassing is
    \subsection{Collection of packages}  
    \label{Collection of packages}
    In this process the cost function will only give an output of the cost that is formed by combining the cost for collecting packages. To optimize the costs a Python script is made such that, when a city is given to be a hub, the code calculates the cost for this specific hub and the cost if the city next in line would be a hub as well. If the total cost drops by adding city as a hub, this city will be added to list of cities that are hubs. If the cost rises, the city will be discarded from the process. If this process is repeated with each time a different starting node, a list will appear of possible combination of hubs and their costs. To illustrate this process the outputs will be stated below in table~\ref{Collection Algorithm} if it were to start with city number 3 as a hub.

    \begin{table}[h!]
        \begin{center}
            \begin{tabular}{||c |c||} 
                \hline
                Cost of the combination(€ x 10^3) & combination of cities as hubs \\ [0.5ex] 
                \hline
                \hline
                169.3 & [3,1]  \\ 
                \hline
                169.8 & [3,2]  \\
                \hline
                169.8 & [3,4]  \\
                \hline
                127.2 & [3,5]  \\ 
                \hline
                132.0 & [3,5,6]  \\
                \hline
                127.4 & [3,5,7]  \\
                \hline
                128.5 & [3,5,8]  \\
                \hline
                124.8 & [3,5,9]  \\
                \hline
                118.7 & [3,5,9,10]  \\
                [1ex] 
                \hline
              \end{tabular}
          \end{center}
        \caption{Exampled of the algorithm which adds cities one by one as hubs based on the cost}
        \label{Collection Algorithm}
    \end{table}

@@

            \begin{table}[h!]
                \begin{center}
                \begin{tabular}{||c|c|c||}
                    \hline
                    \multicolumn{3}{||c||}{Amount of times cities are used as hubs} \\
                    \hline
                    \hline
                    City used as hub & Using only collection cost & Using total cost\\
                    \hline
                    \hline
                    1 &  8 & 5 \\
                    \hline
                    2 & 4   & 11 \\
                    \hline
                    3& 7 & 9\\
                    \hline
                    4  & 1 & 1 \\
                    \hline
                    5 & 8 & 9\\
                    \hline
                    6 & 1 & 8   \\
                    \hline
                    7 & 2& 3 \\
                    \hline
                    8 & 2 & 2 \\
                    \hline
                    9 &  7& 10 \\
                    \hline
                    10 & 11 & 11 \\
                    \hline
                    11 & 1& 2 \\
                    \hline
                    12 & 1 & 1 \\
                    \hline
                    13 & 2& 2 \\
                    \hline
                    14 & 14& 14 \\
                    \hline
                \end{tabular}
                \end{center}
                \caption{Table of the amount of times each city is used as a hub in every combination using the large data set}
                \label{amount of times hubs are used in collection} 
            \end{table}

@@

            When the algorithm is used for different input combinations based on table ~\ref{amount of times hubs are used in collection} the outputs and results show different possible answers with supposedly relative low cost. Hereby the algorithm will add a city as hub if this results in a lower cost by the principle given in the beginning of the section.

            \begin{table}[h!]
                \begin{center}
                    \begin{tabular}{||c|c|c||}
                        \hline
                        \multicolumn{3}{||c||}{Cost and combination of hubs with certain input} \\
                        \hline
                        \hline
                        Input into the algorithm & Output -  collection Cost (€ x 10^3) & Output - total Cost (€ x 10^3)\\
                        \hline
                        \hline
                        [14] &  92.6 | [14, 1, 3] & 166.4 | [14, 1, 2, 3, 5, 7]  \\
                        \hline
                        [10] & 90.0 | [10, 2, 14]   & 153.0 | [10, 2, 14, 8] \\
                        \hline
                        [6, 10]& 93.9 | [6, 10, 14] & 150.4 |  [6, 10, 14]\\
                        \hline
                        [6, 14] &  82.9 | [6, 14]  &  144.5 | [6, 14, 8] \\
                        \hline
                        [9, 14] &  100.7| [9, 14, 1, 3] & 160.4 |  [9, 14, 2, 3, 7] \\
                        \hline
                        [2, 14] & 87.6 | [2, 14, 6] & 156.9 |  [2, 14, 3, 6]\\
                        \hline
                        [2, 10, 14] & 90.0 | [2, 10, 14] & 153.0 | [2, 10, 14, 8]  \\
                        \hline
                    \end{tabular}
                \end{center}
            \caption{Table of the amount of times each city is used as a hub in every combination}
            \label{amount of times hubs are used in collection} 
            \end{table}

@@

             \begin{table}[h!]
                \begin{center}
                \begin{tabular}{||c|c|c||}
                    \hline
                    \multicolumn{3}{||c||}{Amount of times cities are used as hubs} \\
                    \hline
                    City used as hub & Using only collection cost & Using total cost\\
                    \hline
                    1 & 6 & 6 \\
                    \hline
                    2 & 7   & 9\\
                    \hline
                    3& 5& 7\\
                    \hline
                    4  & 2 & 2 \\
                    \hline
                    5 & 4 & 7\\
                    \hline
                    6 & 4 & 8   \\
                    \hline
                    7 & 4& 1 \\
                    \hline
                    8 & 1 & 1 \\
                    \hline
                    9 &  1& 1 \\
                    \hline
                \end{tabular}
                \end{center}
                \caption{Table of the amount of times each city is used as a hub in every combination with the small data set}
                \label{amount of times hubs are used in collection small} 
            \end{table}

            Using this data an estimation is made for the following hubs.

            \begin{table}[h!]
                \begin{center}
                    \begin{tabular}{||c|c|c||}
                        \hline
                        \multicolumn{3}{||c||}{Cost and combination of hubs with certain input} \\
                        \hline
                        Input into the algorithm & Output -  collection Cost (€ x 10^3) & Output - total Cost (€ x 10^3)\\
                        \hline
                        [1] & 35.1| [1,2,3,6] & 52.0| [1, 2, 3, 5, 6]  \\
                        \hline
                        [2] & 34.5 | [2,3,5,7]   & 50.4 | [2,3,5,6] \\
                        \hline
                        [3]& 33.4 | [3,5,7] & 50.4 |  [2,3,5,6]\\
                        \hline
                        [5] &  35.9| [5,1,2,4,6]  &  52.0 | [5,1,2,3,6] \\
                        \hline
                        [7] &  31.5| [7,1] & 50.8 |  [1,2,5,7] \\
                        \hline
                        [6] & 26.3 | [6,2] & 46.3 |  [2,4,6]\\
                        \hline
                        [2, 5] & 33.1 | [2,5,4,6] & 50.4| [2, 5, 3,6]  \\
                        \hline
                    \end{tabular}
                \end{center}
            \caption{Table of the amount of times each city is used as a hub in every combination small data set}
            \label{amount of times hubs are used in collection small} 
            \end{table}

            With the values out of table~\ref{amount of times hubs are used in collection small} it shows that making hubs in cities 2,4 and 6 will give an approximation of the optimal solution. This combination gives a total amount of 46330 euros.

    \subsection{Transfer between hubs} \label{sssec:num1}
        Transport to the same city is free if the city is a hub. To optimize the total cost an algorithm is made that will look at the city with the most flow of parcels to itself and make a hub out of this city. After calculating the cost, the next city with the most flow of parcels to itself will be become a hub. If the solution becomes cheaper by adding a hub, the city is added to a list of hubs. If the total cost increases, nothing happens and the next city (most parcels to itself) becomes a hub. If there are two cities with the same amount of parcels to itself the algorithm will choose the node with the most incoming parcels. Each node will be connected to the hub with the least cost to transport it there, for example if it cost €11 to transport from city 11 to hub 14 and €27 to transport it to hub 2, city 11 will be connected with hub 14. This process is repeated until the algorithm goes through all cities. To illustrate we will use the Large and Small data assignment.
\subsubsection{Result of the large data set}
        \begin{table}[h!]
            \begin{tabular}{||c|c|c||}
                \hline
                nodes that are hubs & flow of parcels to itself (last node) & Total cost (€ x 10^3)\\
                \hline
                [14] &  181 & 182.7 \\
                \hline
                [14,2]   & 39 & 163.5 \\
                \hline
                [14,2,15] & 26 & 169.3 \\
                \hline
                [14,2,15,6]  & 18 & 156.5 \\
                \hline
                [14,2,15,6,13] & 18 & 161.5\\
                \hline
                [14,2,15,6,13,4] & 11 & 167.0   \\
                \hline
                [14,2,15,6,13,4,3] & 9 & 177.1   \\
                \hline
                [14,2,15,6,13,4,3,9] & 9 & 187.7    \\
                \hline
            \end{tabular}
        \caption{Table of nodes that were used as hubs and the associated costs}
        \end{table}

The cheapest situation is when there are 4 hubs in cities 2,6,14 and 15. We connect each city with the hub where the cost to transport a parcel is the lowest, the total cost in this situation would be €156.5 thousand. One can easily see that it is very profitable to make a hub out of city 14, as it is the city with the most incoming parcels (610). In the following subsections we will be looking at the results of the other algorithms and combine those to see if there are similarities.
\subsubsection{Result of the small data set}

        \begin{table}[h!]
            \begin{tabular}{||c|c|c||}
                \hline
                nodes that are hubs & flow of parcels to itself (last node) & Total cost (€ x 10^3)\\
                \hline
                [2] &  39 & 63.6\\
                \hline
                [2,6]   & 18 & 46.5 \\
                \hline
                [2,6,4] & 11 & 46.3 \\
                \hline
                [2,6,4,3]  & 9 & 49.1  \\
                \hline
                [2,6,4,3,7] & 9 & 51.1 \\
                \hline
                [2,6,4,3,7,9] & 9 & 54.2   \\
                \hline
                [2,6,4,3,7,9,5] & 8 & 58.2 \\
                \hline
            \end{tabular}
        \caption{Table of nodes that were used as hubs and the associated costs (Small Data)}
        \end{table}

@@

As can be seen, the distribution costs decrease with each added hub until they reach 0. This is a result of distribution costs from hubs to themselves costs 0. So more of the actual costs are made up of transfer costs as more hubs get added. However, the total costs, displayed in the last column, have quite different results. At first, the costs decrease. But, after adding hub 9 the total costs increase from there onward. So, based on these results, a solution would be to pick hubs 2, 8, 10 and 14 with a total cost of €152.974.

@@

\caption{\centering Order in which the cities got added as hubs by the algorithm based on total costs}
\label{DistAlg2}
\end{table}
\subsubsection{Result of the small data set}
For the small data set, the same algorithm was used. However, the input and programw as slightly modified to fit the small data set. The results can be seen in table \ref{DistAlgSmall1}.

\begin{table}[h]
    \centering
    \begin{tabular}{||c|c|c||}
        \hline
        Chosen hub & Total distribution costs (€ x 10^3)& Total costs (€ x 10^3)  \\
        \hline
        \hline
        6 & 18.4 & 49.3 \\
        \hline
        2 & 13.6 & 46.7 \\
        \hline
        4 & 9.6 & 46.3 \\
        \hline
        5 & 7.2 & 48.4 \\
        \hline
        1 & 5.4 & 50.0 \\
        \hline
        3 & 3.7 & 53.0 \\
        \hline
        8 & 2.2 & 55.3 \\
        \hline
        7 & 1.2 & 58.0 \\
        \hline
        9 & 0.8 & 63.0 \\
        \hline
        10 & 0 & 66.3 \\
        \hline
    \end{tabular}
    \caption{Results based on distribution costs for the small data set}
    \label{DistAlgSmall1}
\end{table}

We see that in this case the optimal solution occurs when hubs 2, 4 and 6 are chosen, with a total cost of €46.330.
Once again, the algorithm was also run based on total costs, the results of which can be seen in table \ref{DistAlgSmall2}.

\begin{table}[h]
    \centering
    \begin{tabular}{||c|c||}
    \hline
        Chosen hub & Total costs (€ x 10^3) \\
        \hline
        \hline
        6 & 49.3 \\
        \hline
        2 & 46.7 \\
        \hline
        4 & 46.3 \\
        \hline
        1 & 48.0 \\
        \hline
        5 & 50.0 \\
        \hline
        7 & 52.1 \\
        \hline
        3 & 54.9 \\
        \hline
        8 & 58.0 \\
        \hline
        9 & 62.9 \\
        \hline
        10 & 66.3 \\
        \hline
    \end{tabular}
    \caption{Results based on total costs for the small data set}
    \label{DistAlgSmall2}
\end{table}

Notably; the first three cities to be added as hubs are the exact same for both cases, with the two after that being switched around. This might suggest that these cities are all good candidates for a hub. We also note that the optimal solution based on total costs is the same, namely hubs 2, 4 and 6 with a total cost of €46.330.

@@

    \subsection{Result of the combined algorithms}
    \subsubsection{Result of the large data set}
    \label{sssec:num2}
By combining and analysing the results of the different algorithms, a hub will be opened at nodes 14 and 6 as these nodes were also hubs in the cheapest situation of all different algorithms that were used. By opening a hub at node 14 the cost for collecting, transferring and distributing can be reduced, as it is the node with the most amount of incoming parcels. The total cost in this situation where we only have two hubs is €144.870. The intuitive algorithm will then go through the nodes one by one and check which combination (with node 14 and 6) is the cheapest, this node will then be added to the list of hubs. This process is repeated until the algorithm goes through all nodes.

\begin{table}[h]
\begin{tabular}{||c |c||}
\hline

Nodes that are hubs & Total cost (€ x 10^3)\\
\hline\hline
[6,14] &  144.8 \\
\hline
[6,8,14]   & 144.5\\
\hline
[2,6,8,14] & 148.1 \\
\hline
[2,5,6,8,14]  & 152.5  \\
\hline
[2,5,6,8,12,14] & 160.3 \\
\hline
\end{tabular}
\caption{Table of nodes that were used as hubs in the initiative algorithm}
\end{table}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[main/.style = {draw, circle,minimum size=0.8cm}]
\node[main] (6) [fill = blue!20] {6};
\node[main] (8) [below right=1.5cm of 6, fill =blue!20] {8};
\node[main] (14) [below left=1.5cm of 6, fill =blue!20] {14};

@@

\subsubsection{Result of the small data set}
By combining and analysing the results of the different algorithms, a hub will be opened at nodes 2, 4 and 6. In the algorithms for both transfer and distribution the combination of these 3 offered the cheapest solution. The algorithm for collection costs does suggest that city 2 and 6 are good candidates as well, though less so for city 4. This results in a total cost of €46.330. Beyond these 3 cities, no other cities were found as viable hubs to make it even cheaper.

Notably, these hubs have the largest flow to themselves. Making them hubs reduces the costs of collecting, transferring and distributing those parcels to €0. Cities 2 and 6 also have some of the most outgoing and incoming parcels, meaning a lot is saved on collection and distribution costs there.

\begin{figure}[h]
\centering
\begin{tikzpicture}[main/.style = {draw, circle,minimum size=0.8cm}]
\node[main] (6) [fill = blue!20] {6};
\node[main] (2) [below right=1.5cm of 6, fill = blue!20] {2};
\node[main] (4) [below left=1.5cm of 6, fill = blue!20] {4};

\node[main] (1) [right=1cm of 2] {1};

\node[main] (3) [above=of 6,xshift=-1.7cm,yshift=-1.7cm] {3};
\node[main] (5) [above=of 6,xshift=-1.3cm,yshift=-0.9cm] {5};
\node[main] (7) [above=of 6,xshift=-0.5cm,yshift=-0.5cm] {7};
\node[main] (8) [above=of 6,xshift=0.5cm,yshift=-0.5cm] {8};
\node[main] (9) [above=of 6,xshift=1.3cm,yshift=-0.9cm] {9};
\node[main] (10) [above=of 6, xshift=1.7cm,yshift=-1.7cm] {10};

\draw[-] (6) -- (4);
\draw[-] (6) -- (2);
\draw[-] (4) -- (2);

\draw[-] (6) -- (3);
\draw[-] (6) -- (5);
\draw[-] (6) -- (7);
\draw[-] (6) -- (8);
\draw[-] (6) -- (9);
\draw[-] (6) -- (10);

\draw[-] (2) -- (1);
\end{tikzpicture}
\caption{A graph of the optimal solution for the small data set}
\end{figure}

@@

\subsection{ILP implementation}
\label{ILPimp}
For the implementation of the ILP the actual values of the inputs will not be used, rather variables to represent any valid input for the ILP. The actual values can be found in <add ref>. A network of n nodes given by the set N represent the city. A city i $\in$ N can be transformed into a hub with cost $f_i$. The amount of packages sent, or flow, from a city i $\in$ N and a city j $\in$ N is given by $w_{ij}$. The cost to send one unit of flow from a city i $\in$ N to a city j $\in$ N is given by $c_{ij}$. It is important to note that the costs are symmetric. That is, $c_{ij} = c_{ji}$ for all i,j $\in$ N. But the flow is not necessarily symmetric. Lastly, there are multipliers for collecting (from city to hub), transfer (from hub to hub) and distribution (from hub to city). These are given the names $\chi$, $\alpha$, $\delta$ respectively.

@@

Next, a means is required that indicates which path is valid for a package to take from a city i to j. A way to do this is by requiring that, for some i,j,k,l $\in$ N, both $e_{ik} = 1$ and $e_{lj} = 1$. However, this would not be linear. Instead we introduce a helper variable $y_{ijkl}$ to mean the same as that:

@@

How this helper variable is made to be the same as what is desired will be done in the constraints.
Using these variables, the objective function and constraints are as follows:

\begin{align}
    min \, z &= \sum^N_{i=1}\sum^N_{j=1}\sum^N_{k=1}\sum^N_{l=1} w_{ij}(\chi c_{ik} + \alpha c_{kl} + \delta c_{lj})y_{ijkl} + \sum^N_{k=1} f_k e_{kk} \label{obj}\\
    \sum^N_{k=1}e_{ik} &= 1 \quad\quad i \in N \label{C1}\\
    e_{ik} & \leq e_{kk} \quad\quad i,k \in N \label{C2}\\
    y_{ijkl} &\leq e_{ik} \quad\quad i,j,k,l \in N \label{C3}\\
    y_{ijkl} &\leq e_{jl} \quad\quad i,j,k,l \in N \label{C4}\\
    y_{ijkl} &\geq e_{ik} + e_{jl} - 1 \quad\quad i,j,k,l \in N \label{C5}\\
    \sum^N_{k=1}e_{kk} &\geq 1 \quad\quad k \in N \label{C6}
\end{align}

The objective function (\ref{obj}) is constructed as follows: given a path from $i \rightarrow k \rightarrow l \rightarrow j$ with i,j,k,l $\in$ N and the relevant multipliers we get that sending one unit of flow over this path is $\chi c_{ik} + \alpha c_{kl} + \delta c_{lj}$. However, we want to send more than just one package. So, it is multiplied by the total flow between the sending city i and receiving city j, namely $w_{ij}$. To make sure that the chosen path is valid, that is city i is assigned to hub k and city j is assigned to hub l, it is also multiplied by $y_{ijkl}$. Finally, we sum over all the indexes i,j,k,l to get the total cost for sending packages.

On top of that, there is also the costs of establishing hubs at certain cities. We multiply this cost for a certain city k $\in$ N by $e_{kk}$, since only hubs are connected to themselves. By summing over k the total costs for establishing hubs is calculated.

The first constraint (\ref{C1}) is there to make sure that each city needs to be assigned to exactly one hub. Similarly, the second constraint (\ref{C2}) makes sure that a city i can only be assigned to a city k if city k itself is a hub.

The next three constraints (\ref{C3}) (\ref{C4}) (\ref{C5}) have been made such that $y_{ijkl} = e_{ik}*e_{lj}$. The validity of this claim is shown in table \ref{tab:Helper}.

@@

Finally, the sixth constraint (\ref{C6}) makes it so that there is at least one hub in the final answer.

\subsection{ILP result}
The ILP model was implemented into Python using PuLP, with CPLEX as solver. The relevant data was imported from an excel file using Pandas. The full program can be found in Appendix \ref{ILPPyth}. 
\subsubsection{Result of the large data set}
After running the program for the large data set it returned an optimal solution of €144.369. Interestingly, the hubs chosen by this program were 6, 8 and 14, the exact same ones as the result from the intuitive algorithm. However, that resulted in a cost of €144.532, which is a difference of 163.

Upon closer inspection, it was discovered that one connection differed from the solution of the intuitive algorithm. In the ILP optimal solution, a graph of which can be found in figure \ref{ILPSol}, city 10 was connected to hub 14 instead of hub 6. The connections between cities 10 and 14 and between 10 and 6 cost the same, namely 9. So the difference in cost is not due to collection or distribution costs, rather it is due to the transfer costs of sending packages through hub 14 instead of 6. The similarity between the two results does suggest that the intuitive algorithm is relatively accurate.
